# Peer Assessment 1

```{r}
data <- read.csv("activity.csv")
str(data)
steps    = data$steps
date     = data$date
interval = data$interval 

# 5 minutes interval means 288 intervals per day

steps.per.day <- aggregate(steps ~ date,data=data,FUN=sum)
barplot(steps.per.day$steps,names.arg=steps.per.day$date,xlab="Date",ylab="Number of Steps")
```

The mean and median steps taken per days given by

```{r}
mean(steps.per.day$steps)
median(steps.per.day$steps)
```

## What is the average daily acivity pattern?

### Time Series Interval of Steps

```{r}
steps.per.interval <- aggregate(steps ~ interval,data=data,FUN=mean)
plot(steps.per.interval$interval,steps.per.interval$steps,type="l",xlab=("Intervals"),ylab="Number of Steps")
```
```{r}
steps.per.interval$interval[which.max(steps.per.interval$steps)]
```

## Imputing Missing Values

### Total Number of missing values. 

```{r}
sum(is.na(data))
```

### Strategy for filling missing values. Since we have the result of the mean number of steps in 5-min intervals, we will use that result to fill the missing values.

```{r}
nas = is.na(data$steps)
data <- merge(data, steps.per.interval, by = "interval", suffixes = c("",".y"))
data$steps[nas] <- data$steps.y[nas]
data <- data[, c(1:3)]
```

### We calculate again de mean and the median

```{r}
steps.per.day1 <- aggregate(steps ~ date,data=data,FUN=sum)
barplot(steps.per.day$steps,names.arg=steps.per.day$date,xlab="Date",ylab="Number of Steps")
```

### The mean and median steps taken per dayis given by

```{r}
mean(steps.per.day1$steps)
median(steps.per.day1$steps)
```

### The impact of the missing data is neglegible, we obtain roughly the same results as without adding missing values. Of course, this is because we added values that are related to the data. If we would have added any other numbers, the mean and median would have probably changed.

## Are there differences in activity patterns between weekdays and weekends?

```{r}
data$days[weekdays(as.Date(data$date)) %in% c("Saturday", "Sunday")] <- "Weekend"
data$days[!weekdays(as.Date(data$date)) %in% c("Saturday", "Sunday")] <- "Weekday"
data$days <- as.factor(data$days)
```

### Make a panel plot containing a time series and the average number of steps taken, averaged accross all weekday days or weekend days

```{r}
steps.per.weekday <- aggregate(steps~interval, data=data, subset
=data$days=="Weekday", FUN=mean)
steps.per.weekend <- aggregate(steps~interval, data=data, subset=data$days=="Weekend", FUN=mean)

par(mfrow=c(2,1))
plot(steps.per.weekday,type="l",main="Weekday")
plot(steps.per.weekend,type="l",main="Weekend")
```
```{r}

